Physcraper: A Python package for continually updated gene trees

### 2020-05-22 phylota-overview.Rmd
phylota citations 91-100

    trees [@mcmahon2015stbase], cites phylota as a databse of gene trees or mul-trees,

@@

    to parallelize BLAST [@yong2010screening], as well as [@meng2014rapidtree] all
    cite phylota as one among other "studies based on data mining large numbers of taxa or loci".

@@

@@

    - A 268 species phylogeny of sharks, representing all orders and 32 families [@sorenson2014effect]

@@

@@

>>>>

    trees [@mcmahon2015stbase; @deepak2013managing], cites phylota as a databse of gene trees or mul-trees,

@@

    to parallelize BLAST [@yong2010screening], as well as @gao2011solution, @li2013partfasttree, and @meng2014rapidtree, all
    cite phylota using the exact same phrase, as one among other "studies based on data mining large numbers of taxa or loci".

@@

    - The [iPTOL project](https://www.researchgate.net/profile/Douglas_Soltis/publication/228815637_Assembling_the_Tree_of_Life_for_the_Plant_Sciences_iPTOL/links/56a7c6bc08aeded22e3700dc.pdf)
    cites phylota as a resource of phylogenetic trees.

@@

    - A 268 species phylogeny of sharks, representing all 8 orders and 32 families [@sorenson2014effect; @sorenson2014evolution]

@@

    - The 10k trees project [@arnold201010ktrees] uses phylota to construct a tree of 301 primate species
    and the outgroup species *Galeopterus variegates*, a tree of 17 extant odd-toed
    ungulates species and the outgroup species *Bos taurus*, and a tree of 70 different
    species of carnivorans and *Equus caballus* as outgroup. However, the do not
    cite it on the paper, but only on their documentation <http://www.academia.edu/download/49690788/10kTrees_Documentation.pdf>.

@@

    - Mentioned in a PHD thesis [@gagnon2016systematique], but not on the final publication [@gagnon2016new],
    phylota was used to state that there are very few sequences available for the Legumes (7,482 out of 19,500 spp) on GenBank's release 194 (Feb2013).
